Strong lensing selection effects

### 2022-08-19 paper/seleff.tex
started discussion

In order for a galaxy-source pair to be included as a strong lens in a survey, three condition must be met.
First of all, part of the source must be multiply imaged.
Second, the multiple images must be detectable.
Third, the lens must be recognised as such.
Each one of these conditions introduces a bias with respect to the parent population of foreground galaxies and background sources. Together, they define the lens detection probability term $\pdet$ of \Eref{eq:one}.

>>>>

In order for a galaxy-source pair to be included as a strong lens in a survey, three condition must be met.
First of all, part of the source must be multiply imaged.
Second, the multiple images must be detectable.
Third, the lens must be recognised as such.
Each one of these conditions introduces a bias with respect to the parent population of foreground galaxies and background sources. Together, they define the lens detection probability term $\pdet$ of \Eref{eq:one}.
%In the best case scenario, the only sources of bias are the first two points.
The first two points are intrinsic to a strong lensing survey and constitute an unavoidable source of bias. 
The best case scenario occurs when the efficiency of including a detected strong lens in a survey is always one. In this case, the third condition does not introduce any further selection and the strong lensing bias is minimised.
We explored this scenario in \Sref{sect:results} when setting the minimum Einstein radius to zero.
